---
title: "Shopify: Question 1"
author: "Mohammad Abbas Meghani"
date: "5/8/2021"
output: html_document
---

## Initial Data Processing

```{r}
# Read Data
data = read.csv("question1.csv")

# Summary
summary(data)

# Convert created_at to Date format
data$created_at = as.Date(data$created_at)

```

### a.  It is very clear that the Naive Average Order Value does not take into account the quantity of orders sold and just does the mean of the order amounts, which is giving an erronous result

```{r }
# Naive AOV
print(head(data))
mean(data$order_amount)
```



### b. A more appropriate quantity would be the average amount per unit sold. This will give us a correct average.

### c. The value is calculated below

```{r}
# Average Amount per order

sum(data$order_amount)/sum(data$total_items)
```


## Supplementary Analysis

Let us check create an order amount per item column and see if the quantity has a relationship with the price.

```{r}
# Plot to see if the order amount has any relationship with items sold

data$avg_order_amt = data$order_amount/data$total_items

plot(data$avg_order_amt,data$total_items,xlab="order amount per item",ylab="number of items",main="Amount per item vs number of items")
```

There seems to be no relationship


### a. Check daily relationship

We aggregate orders by date
```{r}

# Aggregate order_amount by Date to check date relationships

daily_data = aggregate(list(data["order_amount"],data["total_items"]), 
                          by=data["created_at"], sum)
head(daily_data)

# Daily AVerage Amount per Order
daily_data$avg_daily_order_amt = daily_data$order_amount/daily_data$total_items
head(daily_data)
```


Now we see what the average of daily order amount per item sold is and then try to check if any relationship exist between Date and amount
```{r}

# Mean of daily orders

mean(daily_data$avg_daily_order_amt)

plot(daily_data$created_at,daily_data$order_amount,xlab="Date",ylab="Amount",main="Date vs Amount")
```

### b. Check shopwise relationship

```{r}
# Aggregate orders by shop

shop_data = aggregate(list(data["order_amount"],data["total_items"]), 
                       by=data["shop_id"], sum)
head(shop_data)

# Shop AVerage Amount per Order
shop_data$avg_shop_order_amt = shop_data$order_amount/shop_data$total_items
mean(shop_data$avg_shop_order_amt)


```

We check for outliers in the data and find the shop with outlier that needs to be rechecked


```{r}
# Boxplot
boxplot(shop_data$avg_shop_order_amt,main="Boxplot shop order amount per item",ylab="shop order amount per item")

# Outlier shop
shop_data[which.max(shop_data$avg_shop_order_amt),]

```

Shop 78 has a very large outlier which needs to be checked
